### 2016-09-30 domain_specific.tex
Add automatic cross-references to the paper (in rebuttal)
See more at:
http://tex.stackexchange.com/questions/3060/referencing-labels-from-other-files

XXX: Section and footnotes numbers are correct, but my pdf viewer
(evince) doesn't open a new document if I click on them.  I hope,
this is a bug.
"domain specific" to "domain specific physics"
Clearer wording

SymPy includes several submodules that allow users to solve domain specific
problems. For example, a comprehensive physics submodule is included that is
useful for solving problems in mechanics, optics, and quantum
mechanics along with support for manipulating physical quantities with units.

@@

The \verb|sympy.physics.vector| submodule provides reference frame-, time-,
and space-aware vector and dyadic objects that allow for three-dimensional
operations such as addition, subtraction, scalar multiplication, inner and
outer products, and cross products. The vector and dyadic objects can both be
written in very compact notation that make it easy to express the vectors and
dyadics in terms of multiple reference frames with arbitrarily defined
relative orientations. The vectors are used to specify the positions,
velocities, and accelerations of points; orientations, angular velocities, and
angular accelerations of reference frames; and forces and torques. The dyadics
are essentially reference frame-aware $3 \times 3$
tensors~\cite{tai1997generalized}. The vector and dyadic objects can be used
for any one-, two-, or three-dimensional vector algebra, and they provide a
strong framework for building physics and engineering tools.

@@

\subsection{Quantum Mechanics}

>>>>

SymPy includes several submodules that allow users to solve domain specific
physics problems. For example, a comprehensive physics submodule is included
that is useful for solving problems in mechanics, optics, and quantum
mechanics along with support for manipulating physical quantities with units.

@@

The \verb|sympy.physics.vector| submodule provides reference frame-, time-,
and space-aware vector and dyadic objects that allow for three-dimensional
operations such as addition, subtraction, scalar multiplication, inner and
outer products, and cross products. The vector and dyadic objects both can be
written in very compact notation that make it easy to express the vectors and
dyadics in terms of multiple reference frames with arbitrarily defined
relative orientations. The vectors are used to specify the positions,
velocities, and accelerations of points; orientations, angular velocities, and
angular accelerations of reference frames; and forces and torques. The dyadics
are essentially reference frame-aware $3 \times 3$
tensors~\cite{tai1997generalized}. The vector and dyadic objects can be used
for any one-, two-, or three-dimensional vector algebra, and they provide a
strong framework for building physics and engineering tools.

@@

\subsection{Quantum Mechanics}
\label{sec:quantum}
